% !TEX root = ../resume.tex
%-----------EXPERIENCE (MASTER)-----------%
% All real experience. Agent selects from this for tailoring.
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {High Performance Computing (HPC) Engineering Intern}{May 2026 -- Present}
    {Los Alamos National Laboratory}{Los Alamos, NM}
    \resumeItemListStart
        \resumeItem{Designed and deployed a hardware telemetry pipeline using Redfish API, Kafka, InfluxDB, and Telegraf, collecting 830K+ data points daily with zero data loss through containerized microservices and systemd automation.}
        \resumeItem{Built real-time data pipeline streaming 34,560 metrics/hour from a multi-node cluster to Kafka, InfluxDB, and JSON files with automated retention policies, implementing Telegraf JSON parsers and multidimensional tagging for Grafana dashboard analysis.}
        % \resumeItem{Architected hybrid GET/POST Redfish polling system for hardware health monitoring after resolving firmware limitations, achieving 0.10\% CPU footprint by aggregating 7 sensors per request while maintaining real-time alerting for 144 sensors across 9 compute nodes.}
        % \resumeItem{Automated deployment and monitoring of 9-node telemetry system with 59 Bash scripts (5,568 lines), systemd services with fault isolation, cron-based health checks validating data freshness (<60s), and containerized microservices using Podman, achieving 100\% uptime with zero manual interventions.}
        \resumeItem{Reverse-engineered Intel Redfish API, implementing TelemetryService polling and EventService subscriptions across 6 endpoint families with a Python Flask receiver using dual-write pattern (Kafka + file storage).}
        \resumeItem{Provisioned a multi-node Rocky Linux cluster using OpenCHAMI, automating OS deployment via Kickstart and cloud-init, and implementing a GitLab CI/CD pipeline to automatically build and test boot images on commit.}
    \resumeItemListEnd

    \resumeSubheading
    {Extended Reality (XR) Developer}{July 2024 -- May 2026}
    {Mesh Labs (formerly Meteor Studio)}{Mesa, AZ}
    \resumeItemListStart
        \resumeItem{Containerized a GPU-enabled multi-dependency environment using Docker Compose, reducing setup time from 60 to 16 minutes and eliminating Linux/WSL2 compatibility issues.}
        \resumeItem{Developed a Python volumetric rendering and 3D camera calibration pipeline using RANSAC-based feature matching and ICP point cloud registration for research prototype applications.}
        \resumeItem{Implemented core Blueprint-based interaction and UI systems in UE5 for a VR training simulation, including MetaHuman spatial audio and character switching.}
    \resumeItemListEnd

    \resumeSubheading
    {Undergraduate Researcher}{June 2023 -- August 2023}
    {Texas A\&M-Corpus Christi}{Corpus Christi, TX}
    \resumeItemListStart
        \resumeItem{Developed multi-drone control system for PX4 drones in Gazebo simulation, debugging timing and communication across hardware/software boundaries while coordinating up to 10 autonomous drones.}
        \resumeItem{Designed windowing-based preprocessing pipelines for time-series sensor data, trained and validated KNN, SVM, Random Forest, and Naive Bayes ensemble models, improving gesture recognition accuracy by 10\%.}
        \resumeItem{Co-authored research published in ACM Digital Library and ICICT 2024.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
