%-----------PROJECTS (MASTER)-----------%
% All real projects. Agent selects from this for tailoring.
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{AI-Integrated Wireless Emergency Alerts}}{}
    \resumeItemListStart
        \resumeItem{Engineered a FastAPI microservice integrating retrieval-augmented generation (RAG) with ChromaDB to enable semantic search and context-aware LLM responses.}
        \resumeItem{Designed a containerized automation system with custom scheduling and health endpoints to orchestrate data ingestion, scraping, and LLM pipelines.}
        \resumeItem{Developed a fault-tolerant Python scraper for the PBS WARN API, utilizing exponential backoff to reliably extract and normalize live emergency data.}
        \resumeItem{Built an automated vector database cleanup service to dynamically prune expired alerts, optimizing retrieval fidelity and reducing database bloat.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{gRPC Microservices System}}{}
    \resumeItemListStart
        \resumeItem{Architected a distributed system with 5 gRPC-based microservices, implementing both interactive CLI and automated client interfaces with robust error handling and modular service design.}
        \resumeItem{Implemented 5 gRPC services (Fitness, RecipeBook, Sort, Joke, Echo) with Protocol Buffers, file-based persistence, a service registry for discovery, and thread-safe concurrent request handling.}
        \resumeItem{Deployed system on AWS EC2 instance with public accessibility, enabling multi-client access and validating concurrent service requests.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{MotoMart WebUI}}{}
    \resumeItemListStart
        \resumeItem{Built a React vehicle marketplace SPA with React Router and Axios integration against a .NET 8 REST backend, refactoring the vehicle details component with CSS modules for enhanced attribute display.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Gym Calendar Application (Memoranda) Modernization}}{}
    \resumeItemListStart
        \resumeItem{Integrated Google Calendar API with OAuth2 to synchronize cross-timezone class schedules, implementing push-based event creation and resolving datetime offset conflicts.}
        \resumeItem{Modernized the itinerary UI to improve usability, tailoring agenda views for students and trainers to display only relevant classes and sessions.}
        \resumeItem{Refactored legacy Java codebase (25,000+ LOC) to eliminate compiler warnings and improve maintainability while managing Git workflows and merge conflicts.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Clustering Analysis of Steam Games Using Reviews, Sentiments, and Metadata}}{}
    \resumeItemListStart
        \resumeItem{Conducted clustering analysis with Python on 42,497 Steam games using K-Means and Agglomerative Clustering with custom distance metrics, documenting process and findings in academic paper format.}
        \resumeItem{Scraped and analyzed sentiment from 385 games' English reviews using VADER and vectorized text with BERT embeddings, transforming Steamworks API JSON data into structured formats.}
        \resumeItem{Built a modular Python pipeline for data collection, preprocessing, and ML analysis using pandas, scikit-learn, and transformers, with Git LFS for large data.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Distributed Parallel Sum System}}{}
    \resumeItemListStart
        \resumeItem{Architected a leader-coordinated distributed computation system that splits integer arrays across 3 worker nodes using ExecutorService thread pools, achieving a 2.6x speedup over sequential execution (934ms to 353ms).}
        \resumeItem{Implemented cross-verification consensus where each node recomputes another node's partition to validate correctness, and designed a fault injection flag enabling intentional errors to verify the consensus mechanism detected corrupted partial sums.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Protobuf-Based Sudoku Game Server}}{}
    \resumeItemListStart
        \resumeItem{Built a multi-client Sudoku game server with a custom 18-message Protocol Buffers protocol (6 request types, 7 response types, 11 evaluation types), handling concurrent player sessions with thread-safe scoring and file-based leaderboard persistence.}
        \resumeItem{Designed a state machine-based client-server protocol directing gameplay flow, with configurable difficulty (1--20), board clear operations (cell/row/column/grid), and a persistent leaderboard surviving server restarts.}
        \resumeItem{Deployed server on AWS EC2 for multi-client public access, validating concurrent gameplay and protocol robustness across remote connections.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
